A-maze of Natural Stories: Texts are comprehensible using the Maze task

### 2022-08-18 Papers/Paper/manuscript.Rmd
small tweaks by roger

We created a set of predictor variables of frequency, word length, and surprisals from 4 language models.  For length, we used the length in characters excluding end punctuation. For unigram frequency, we tokenized the training data from @gulordava18 and tallied up instances. We then rescaled the word counts to get the log2 frequency of occurrences per 1 billion words, so higher values indicate higher log frequencies. We got per-word surprisals for each of 4 different language models, covering a range of common architectures: a Kneser-Ney smoothed 5-gram, GRNN [@gulordava18], Transformer-XL [@daiTransformerXLAttentiveLanguage2019], and GPT-2 [@radfordLanguageModelsAre], using lm-zoo [@gauthierSyntaxGymOnlinePlatform2020].  For all of these predictors, we used both the predictor at the current word as well as lagged predictors from the previous word.

>>>>

We created a set of predictor variables of frequency, word length, and surprisals from 4 language models.  For length, we used the length in characters excluding end punctuation. For unigram frequency, we tokenized the training data from @gulordava18 and tallied up instances. We then rescaled the word counts to get the log2 frequency of occurrences per 1 billion words, so higher values indicate higher log frequencies. We got per-word surprisals for each of 4 different language models, covering a range of common architectures: a Kneser-Ney smoothed 5-gram; the long short-term memory recurrent neural network model of @gulordava18, which we refer to as GRNNN; Transformer-XL [@daiTransformerXLAttentiveLanguage2019]; and GPT-2 [@radfordLanguageModelsAre], using lm-zoo [@gauthierSyntaxGymOnlinePlatform2020].  For all of these predictors, we used both the predictor at the current word as well as lagged predictors from the previous word.
